The yaq Project: \\ Standardized Software Enabling Flexible Instrumentation

### 2023-02-06 paper.tex
preemptive

In \yaq{}, communication between daemons and clients is performed over TCP/IP using Apache Avro RPC \cite{AvroSpecification}.
Avro provides an agreed upon standard for efficient serialization of data and method calls from a remote (client) process.
Practically, the \yaq{} interface looks like a collection of methods or functions, which Avro calls ``messages''.
Each message has defined input parameters and output return types.
A sensor might implement a message called ``\texttt{get\_measured}'' which takes no parameters and returns a dictionary mapping channel names to numeric or array data.
A motor would implement a pair of messages for setting and reading back the motor position: ``\texttt{set\_position(float position)} $\rightarrow$ \texttt{null}'' and ``\texttt{get\_position()} $\rightarrow$ \texttt{float}''.
Messages make up the lowest level functionality of the \yaq{} interface.
Each individual communication between client and daemon involves one message being requested by the client and the response returned from the daemon.
Each daemon supports a collection of messages for its unique functionality, called the ``protocol''.
When a client first connects to a daemon over TCP/IP, the daemon provides a complete description of its own protocol.
We therefore refer to the daemons as ``self-describing''.

@@

We have carefully defined \yaq{} traits to maximize interoperability while not excluding hardware with unusual features.
New traits can be discussed by the community through the yaq enhancement proposal system.
We are somewhat conservative about adding new traits, and it's crucial that multiple hardware interface examples be considered when defining traits.
Configuration that is unique to a single interface is best handled through protocol-specific messages.
For example, our protocol for interfacing with data acquisition cards from Gage provides a message for setting the segment count.
Unique messages are avaliable through script-based and graphical clients, but usage of such messages in scripts naturally limits portability.

>>>>

In \yaq{}, communication between daemons and clients is performed over TCP/IP using Apache Avro RPC \cite{AvroSpecification}.
Avro provides an agreed upon standard for efficient serialization of data and method calls from a remote (client) process.
Practically, the \yaq{} interface looks like a collection of methods or functions, which Avro calls ``messages''.
Each message has defined input parameters and output return types.
A sensor might implement a message called ``\texttt{get\_measured}'' which takes no parameters and returns a dictionary mapping channel names to numeric or array data.
A motor would implement a pair of messages for setting and reading back the motor position: ``\texttt{set\_position(float position)} $\rightarrow$ \texttt{null}'' and ``\texttt{get\_position()} $\rightarrow$ \texttt{float}''.
Messages make up the lowest level functionality of the \yaq{} interface.
Each individual communication between client and daemon involves one message being requested by the client and the response returned from the daemon.
If multiple messages are sent simultaneously, the daemon processes one message at a time.
The protocol is preemptive: in the case of a conflict, the daemon will obey the last message to arrive.
Each daemon supports a collection of messages for its unique functionality, called the ``protocol''.
When a client first connects to a daemon over TCP/IP, the daemon provides a complete description of its own protocol.
We therefore refer to the daemons as ``self-describing''.

@@

We have carefully defined \yaq{} traits to maximize interoperability while not excluding hardware with unusual features.
New traits can be discussed by the community through the yaq enhancement proposal system.
It's crucial that multiple hardware interface examples be considered when defining traits.
Configuration that is unique to a single interface is best handled through protocol-specific messages.
For example, our protocol for interfacing with data acquisition cards from Gage provides a message for setting the segment count.
Unique messages are avaliable through script-based and graphical clients, but usage of such messages in scripts naturally limits portability.
